### 2020-04-29 README.Rmd
Update results for Leeds
Heads-up @joeytalbot

roads_top %>%
  st_drop_geometry() %>% 
  knitr::kable(digits = 0)
```

@@

```{r}
roads = rsf %>% filter(region == "Leeds", pctgov > 100)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.zoom.limits = c(12, 13)) + tm_scale_bar()
```

@@

roads_top %>%
  st_drop_geometry() %>% 
  knitr::kable(digits = 0)
```

>>>>

roads_top %>%
  st_drop_geometry() %>% 
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>% knitr::kable(digits = 0)
```

@@

```{r}
roads = rsf %>% filter(region == "Leeds", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Leeds", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 3000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_scale_bar()
```

@@

```{r}
region_centre = tmaptools::geocode_OSM("Leeds", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 3000)
roads_top = roads %>%
  filter(length > 300) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.view = 13) + tm_scale_bar()

roads_top %>%
  st_drop_geometry() %>% 
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>% knitr::kable(digits = 0)
```
